---
title: "FASOM Results"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: TRUE
    toc_depth: 3
    code_folding: "hide"
    number_sections: TRUE
---
# Setup
```{r setup, include=FALSE}
devtools::load_all(".")
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 10, fig.height = 6, dpi = 150)
```

```{r setup-filters, include=FALSE}
# Model names to filter report (bare GDX basenames, no `.gdx`).
model_filter = c("V43t6_Ag", "V43t6_For")
```

```{r process-data, include=FALSE}
# Process GDX files to standard CSV format (skips if files already exist).
# Set force = TRUE to re-process after data updates.
process_fasom_gdx(force = FALSE)
```

```{r helpers}
# GHG Pool mapping: variable -> pool label (for ghg_report and ghg_regional)
.ghg_pool_dt <- read.csv(here::here("data-raw", "VariableMapping", "FASOM_submap_ghg_pool.csv"))
GHG_POOL_MAP <- setNames(.ghg_pool_dt$ghg_pool, .ghg_pool_dt$variable)

# Commodity group lookup for ag_balance (acompareBalancep)
.comm_dt <- read.csv(here::here("data-raw", "VariableMapping", "FASOM_submap_commodity_group.csv"))
CROPS_COMMODITIES     <- .comm_dt$commodity[.comm_dt$group == "crop"]
LIVESTOCK_COMMODITIES <- .comm_dt$commodity[.comm_dt$group == "livestock"]
```

## Data Access

```{r load-data, message=FALSE, warning=FALSE}
carbon_price  <- read_dataset("carbon_price.csv",  model_filter = model_filter)
ghg_summary   <- read_dataset("ghg_summary.csv",   model_filter = model_filter)
ghg_report    <- read_dataset("ghg_report.csv",    model_filter = model_filter) %>%
  mutate(ghg_pool = GHG_POOL_MAP[variable])
ag_strategies <- read_dataset("ag_strategies.csv", model_filter = model_filter)
ag_summary    <- read_dataset("ag_summary.csv",    model_filter = model_filter)
ag_balance    <- read_dataset("ag_balance.csv",    model_filter = model_filter)
ag_proc_biod  <- read_dataset("ag_proc_biod.csv",  model_filter = model_filter)
ag_proc_elec  <- read_dataset("ag_proc_elec.csv",  model_filter = model_filter)
ag_proc_eth   <- read_dataset("ag_proc_eth.csv",   model_filter = model_filter)

for_product_price  <- read_dataset("for_product_price.csv",  model_filter = model_filter)
total_acres        <- read_dataset("total_acres.csv",        model_filter = model_filter)
nat_log_harvest    <- read_dataset("nat_log_harvest.csv",    model_filter = model_filter)
mfg_output         <- read_dataset("mfg_output.csv",         model_filter = model_filter)
recycling_output   <- read_dataset("recycling_output.csv",   model_filter = model_filter)
land_transfer      <- read_dataset("land_transfer.csv",      model_filter = model_filter)
total_for_acres    <- read_dataset("total_for_acres.csv",    model_filter = model_filter)
chk_eq_landbalance <- read_dataset("chk_eq_landbalance.csv", model_filter = model_filter)
```

# Carbon Prices {#carbon-prices}

*Data: carbon_price.csv*
## Carbon Price {#cp-sheet1-2}

```{r cp-sheet1-2}
plotting(
  df         = carbon_price %>% mutate(value = value / (44 / 12)) %>% filter(scenario != "BASE") %>% mutate(scenstart = as.numeric(str_sub(scenario, start = 2, end = -4))),
  figtype    = "timeseries",
  fb_title_name = "Carbon Price (2020–2050)",
  fb_figure_no  = "1.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2050",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "scenstart",
  fb_y_units = "$/t CO2e",
  fb_subtitle = "Non-baseline scenarios, faceted by starting price ($/t CO2)",
  fb_caption  = paste0("Data: carbon_price.csv\nModels: ", paste0(model_filter, collapse = ", ")),
  fb_points   = TRUE
)
```

# National GHG Summary {#ghg-summary}

```{r ghg-summary-base-data}
ghg_sum_annual <- ghg_summary %>% 
  dplyr::filter(set == "annualflux", gas == "carbondioxideeq", category == "AllTotal", scenario == "BASE")

ghg_sum_level  <- ghg_summary %>% 
  dplyr::filter(set == "level", gas == "carbondioxideeq", category == "AllTotal")
```

## Annual Flux {#ghg-sum-brflux}

```{r ghg-sum-brflux}
br_flux_df <- 
  ghg_sum_annual %>%
  mutate(value = value / 1000) %>%
  filter(!(variable %in% c("TotalNetEmis"))) %>%
  filter(!grepl("BioElec", variable)) %>%
  filter(!grepl("Biodiesel", variable)) %>% 
  filter(!grepl("Ethl", variable)) %>% 
  mutate(highlevel = str_extract(variable, "[^_]+")) %>% 
  filter(highlevel != "Dev")

# TODO: Label quants within bars

plotting(
  df         = br_flux_df,
  figtype    = "stacked_bar",
  fb_title_name = "Baseline Annual Flux",
  fb_figure_no  = "2.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "highlevel",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_y_title = "Average Annual Flux",
  fb_y_units = "Tg CO2e/year",
  fb_options = c("Aggregate variables"),
  fb_subtitle = "V43t6_Ag baseline; GHG pools grouped by high-level category",
  fb_caption  = paste0("Data: ghg_summary.csv (annualflux, carbondioxideeq, AllTotal)\nModels: ", paste0(model_filter, collapse = ", ")),
  fb_labels   = TRUE
)
```

```{r ghg-breakdown-brflux}
for (hl in unique(br_flux_df$highlevel)) {
  hl_p <- plotting(
    df         = br_flux_df %>% filter(highlevel == hl),
    figtype    = "stacked_bar",
    fb_title_name = paste0("Baseline Annual Flux (", hl, ")"),
    fb_figure_no  = "2.1",
    fb_x       = "year",
    fb_y       = "value",
    fb_color   = "variable",
    fb_regions = NULL,
    fb_models  = c("V43t6_Ag"),
    fb_years   = "2020-2065",
    fb_scenarios = c("BASE"),
    fb_variable  = NULL,
    fb_y_title = "Average Annual Flux",
    fb_y_units = "Tg CO2e/year",
    fb_subtitle = paste0("V43t6_Ag baseline; individual GHG variables within '", hl, "'"),
    fb_caption  = paste0("Data: ghg_summary.csv (annualflux, carbondioxideeq, AllTotal)\nModels: ", paste0(model_filter, collapse = ", ")),
    fb_labels   = TRUE
  )
  
  print(hl_p)
}
```

```{r ghg-sum-baseflux2}
plotting(
  df         = ghg_sum_annual %>%  mutate(value = value / 1e6) %>%  filter(variable == "TotalNetEmis"),
  figtype    = "timeseries",
  fb_title_name = "Annual GHG Flux — Baseline Total Net Emissions",
  fb_figure_no  = "2.4",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_y_title  = "Net Emissions",
  fb_y_units  = "MMT CO2e",
  fb_subtitle = "Baseline scenario; TotalNetEmis across active models",
  fb_caption  = "Data: ghg_summary.csv",
  fb_hline0   = TRUE,
  fb_points   = TRUE
)
```
## Mitigation Potential

```{r ghg-sum-remaining}
# Check that this is pointing at the right values

plotting(
  df         = ghg_sum_level %>% mutate(value = value / 1e9) %>% dplyr::filter(variable == "TotalNetEmis"),
  figtype    = "timeseries",
  fb_title_name = "Cumulative GHG Mitigation",
  fb_figure_no  = "2.12",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2025-2065",
  fb_scenarios = c("$20at3", "$35at3", "$50at3", "BASE"),
  fb_variable  = NULL,
  fb_y_title  = "Cumulative Net Emissions",
  fb_y_units  = "BMT CO2e",
  fb_subtitle = "V43t6_Ag; cumulative TotalNetEmis by carbon-price scenario",
  fb_caption  = "Data: ghg_summary.csv (set = level)",
  fb_hline0   = TRUE,
  fb_points   = TRUE,
  fb_facet1 = "scenario",
  fb_labels = TRUE
)
```
# Agriculture Balance {#ag-balance}

```{r ag-bal-setup}
crops_in_data <- unique(ag_balance$commodity[
  ag_balance$commodity %in% CROPS_COMMODITIES])

livestock_in_data <- unique(ag_balance$commodity[
  ag_balance$commodity %in% LIVESTOCK_COMMODITIES])
```

## Average Wheat Price {#ag-bal-wheat-price}

```{r ag-bal-wheat-price}
wheat_df <- 
  ag_balance %>% 
  filter(variable == "PriceX100", commodity %in% c("DurumWheat","HardRedSpringWheat","HardRedWinterWheat", "SoftRedWinterWheat","SoftWhiteWheat")) %>%
  mutate(value = value / 100) %>% 
  mutate(scenstart = as.numeric(str_sub(scenario, start = 2, end = -4)))

hl_p <- 
  plotting(
    wheat_df %>% filter(scenario == "BASE"),
    fb_title_name = paste0("Wheat Price (Baseline Type Comparison)"),
    figtype    = "timeseries",
    fb_figure_no  = "6.1",
    fb_x       = "year",
    fb_y       = "value",
    fb_color   = "commodity",
    fb_regions = NULL,
    fb_models  = c("V43t6_Ag"),
    fb_years   = "2015-2100",
    fb_scenarios = NULL,
    fb_variable  = NULL,
    fb_y_title  = "Price",
    fb_y_units  = "$/unit",
    fb_subtitle = "V43t6_Ag baseline; comparison across wheat types",
    fb_caption  = "Data: ag_balance.csv (variable = PriceX100)"
  )
  
print(hl_p)

for (hl in unique(wheat_df$commodity)) {
  hl_p <- plotting(
    wheat_df %>% filter((commodity == hl) & (scenario != "BASE")),
    fb_title_name = paste0("Wheat Price (", hl, ")"),
    figtype    = "timeseries",
    fb_figure_no  = "6.1",
    fb_x       = "year",
    fb_y       = "value",
    fb_color   = "scenario",
    fb_regions = NULL,
    fb_models  = c("V43t6_Ag"),
    fb_years   = "2015-2100",
    fb_scenarios = NULL,
    fb_variable  = NULL,
    fb_y_title  = "Price",
    fb_y_units  = "$/unit",
    fb_facet1   = "scenstart",
    fb_subtitle = paste0("V43t6_Ag; ", hl, " price by scenario, faceted by starting carbon price"),
    fb_caption  = "Data: ag_balance.csv (variable = PriceX100)"
  )
  
 print(hl_p)
}
```

## Crop Domestic Demand {#ag-bal-domdem-crops}

```{r ag-bal-domdem-crops}
# TODO: Verify units here

plotting(
  df         = ag_balance %>%
    filter(variable == "Dom-Demand",
           commodity %in% crops_in_data,
           scenario == "BASE"),
  figtype    = "timeseries",
  fb_title_name = "Domestic Demand for Crops",
  fb_figure_no  = "6.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2100",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "commodity",
  fb_y_title  = "Domestic Demand",
  fb_subtitle = "Baseline scenario; crop commodities, faceted by commodity",
  fb_caption  = "Data: ag_balance.csv (variable = Dom-Demand)"
)
```

## Livestock Domestic Demand {#ag-bal-domdem-livestock}

```{r ag-bal-domdem-livestock}
plotting(
  df         = ag_balance %>%
    filter(variable == "Dom-Demand",
           commodity %in% livestock_in_data,
           scenario == "BASE"),
  figtype    = "timeseries",
  fb_title_name = "Domestic Demand for Livestock",
  fb_figure_no  = "6.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2015-2100",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "commodity",
  fb_y_title  = "Domestic Demand",
  fb_subtitle = "V43t6_Ag baseline; livestock commodities, faceted by commodity",
  fb_caption  = "Data: ag_balance.csv (variable = Dom-Demand)"
)
```

## Livestock Exports {#ag-bal-export}

```{r ag-bal-export}
plotting(
  df         = ag_balance %>%
    filter(variable == "Export",
           commodity %in% livestock_in_data,
           scenario == "BASE"),
  figtype    = "timeseries",
  fb_title_name = "Livestock Exports",
  fb_figure_no  = "6.4",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2100",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "commodity",
  fb_y_title  = "Exports",
  fb_subtitle = "Baseline scenario; livestock commodities across active models",
  fb_caption  = "Data: ag_balance.csv (variable = Export)"
)
```

## Crop Prices {#ag-bal-price}

```{r ag-bal-price}
# TODO: Fix scaling

plotting(
  df         = ag_balance %>%
    filter(variable == "PriceX100",
           commodity %in% crops_in_data) %>%
    mutate(value = value / 100),
  figtype    = "timeseries",
  fb_title_name = "Baseline Crop Prices",
  fb_figure_no  = "6.7",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2100",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_facet1  = "commodity",
  fb_y_title  = "Price",
  fb_y_units  = "$/unit",
  fb_subtitle = "Baseline scenario; crop commodities across active models",
  fb_caption  = "Data: ag_balance.csv (variable = PriceX100, scaled /100)"
)
```

## Livestock Prices {#ag-bal-price2}

```{r ag-bal-price2}
plotting(
  df         = ag_balance %>%
    filter(variable == "PriceX100",
           commodity %in% livestock_in_data) %>%
    mutate(value = value / 100),
  figtype    = "timeseries",
  fb_title_name = "Livestock Prices",
  fb_figure_no  = "6.8",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2015-2100",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_facet1  = "commodity",
  fb_y_title  = "Price",
  fb_y_units  = "$/unit",
  fb_subtitle = "V43t6_Ag baseline; livestock commodities, faceted by commodity",
  fb_caption  = "Data: ag_balance.csv (variable = PriceX100, scaled /100)"
)
```

## Soybean Production {#ag-bal-production}

```{r ag-bal-production}
# TODO: Verify units

plotting(
  df         = ag_balance %>%
    filter(commodity == "SoybeanMeal",
           !variable %in% c("Excess","Export","PriceX100","Proc-Use","Proc-Yld","Prod-Use")),
  figtype    = "timeseries",
  fb_title_name = "Soybean Meal Balance",
  fb_figure_no  = "6.11",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2015-2100",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "variable",
  fb_subtitle = "V43t6_Ag; balance components (excl. price/process), faceted by variable",
  fb_caption  = "Data: ag_balance.csv (commodity = SoybeanMeal)"
)
```

# Biodiesel {#ag-proc-biod}

## Biodiesel by Process {#ag-biod-sheet1}

```{r ag-biod-sheet1}
plotting(
  df         = ag_proc_biod %>%
    filter(region == "Total",
           variable != "Make_Tot_Biodiesel_from_BD"),
  figtype    = "timeseries",
  fb_title_name = "Biodiesel Production by Process",
  fb_figure_no  = "7.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2050",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_facet1 = "variable",
  fb_subtitle = "V43t6_Ag baseline; national totals by feedstock process",
  fb_caption  = "Data: ag_proc_biod.csv (region = Total)"
)
```

## Aggregated Biodiesel  {#ag-biod-sheet1-2}

```{r ag-biod-sheet1-2}
plotting(
  df         = ag_proc_biod %>%
    filter(region == "Total",
           variable != "Make_Tot_Biodiesel_from_BD"),
  figtype    = "stacked_bar",
  fb_title_name = "Total Biodiesel Production",
  fb_figure_no  = "7.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2050",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_subtitle = "Baseline scenario; stacked by feedstock process",
  fb_caption  = "Data: ag_proc_biod.csv (region = Total)",
  fb_labels   = TRUE
)
```

# Bioenergy {#ag-proc-elec}

## Electricity by Process {#ag-elec-levels}

```{r ag-elec-levels}
# TODO: Determine how to aggregate these values

plotting(
  df         = ag_proc_elec %>%
    filter(region == "Total"),
  figtype    = "timeseries",
  fb_title_name = "Electricity from Bioenergy by Process",
  fb_figure_no  = "8.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2015-2050",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_subtitle = "V43t6_Ag baseline; national totals by process",
  fb_caption  = "Data: ag_proc_elec.csv (region = Total)"
)
```

```{r ag-elec-levels3}
plotting(
  df         = ag_proc_elec %>%
    group_by(year, scenario, model) %>%
    summarise(value = sum(value, na.rm = TRUE), .groups = "drop") %>%
    mutate(variable = "Total Bioelectricity"),
  figtype    = "timeseries",
  fb_title_name = "Total Bioelectricity Production",
  fb_figure_no  = "8.6",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2015-2050",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_subtitle = "V43t6_Ag baseline; aggregated across processes",
  fb_caption  = "Data: ag_proc_elec.csv (summed over variable)",
  fb_points   = TRUE,
  fb_labels   = TRUE
)
```
## Difference from 2100 Level {#ag-elec-diff2100}

```{r ag-elec-diff2100}

```

# Ethanol {#ag-proc-eth}

## Ethanol by Process {#ag-eth-sheet1}

```{r ag-eth-sheet1}
plotting(
  df         = ag_proc_eth %>%
    filter(region == "Total"),
  figtype    = "timeseries",
  fb_title_name = "Ethanol Production by Process",
  fb_figure_no  = "9.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2015-2100",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_subtitle = "V43t6_Ag baseline; national totals by feedstock process",
  fb_caption  = "Data: ag_proc_eth.csv (region = Total)"
)
```

# Land Balance Check {#chk-landbalance}

```{r chk-landbal-setup}
chk_lb <- chk_eq_landbalance %>%
  filter(scenario == "BASE") %>%
  group_by(year, region, forest_type, variable, model) %>%
  summarise(value = sum(value, na.rm = TRUE), .groups = "drop") %>%
  mutate(scenario = "BASE")
```

## Demand to Ag by Forest Type {#chk-lb-demand-toag}

```{r chk-lb-demand-toag}
plotting(
  df         = chk_lb %>%
    filter(variable == "demand_toag"),
  figtype    = "stacked_bar",
  fb_title_name = "Land Demand To Agriculture by Forest Type",
  fb_figure_no  = "10.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "forest_type",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2100",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_subtitle = "Baseline scenario; land moving from forest to agriculture, stacked by forest type",
  fb_caption  = "Data: chk_eq_landbalance.csv (variable = demand_toag)",
  fb_labels   = TRUE
)
```

## Overview — All Measures {#chk-lb-overview}

```{r chk-lb-overview}
plotting(
  df         = chk_lb %>%
    filter(variable != "demand_todev") %>%
    group_by(year, variable, scenario, model) %>%
    summarise(value = sum(value, na.rm = TRUE), .groups = "drop"),
  figtype    = "timeseries",
  fb_title_name = "Land Balance Check - All Measures",
  fb_figure_no  = "10.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2100",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_facet1  = "variable"
)
```

## Supply Affor by Forest Type {#chk-lb-supply-affor}

```{r chk-lb-supply-affor}
# Tableau: chk_eq_landbalance.twb / supply affor by for_type
# Rows: Measure; Value, Cols: Model; Year, Color: ForType
# Filter: Measure=supply_affor, Scenario=Base
plotting(
  df         = chk_lb %>%
    filter(variable == "supply_affor"),
  figtype    = "stacked_bar",
  fb_title_name = "Afforestation Supply by Forest Type",
  fb_figure_no  = "10.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "forest_type",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2100",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL
)
```

# Forest Product Prices {#for-product-prices}

*Source: For_Product_Prices.twb — data: for_product_price.csv*

## Lumber & Plywood {#for-pp-lumber}

```{r for-pp-lumber}
plotting(
  df         = for_product_price %>%
    filter(variable %in% c("HW_Lumber","HW_Plywood","SW_Lumber","SW_Plywood")),
  figtype    = "timeseries",
  fb_title_name = "Lumber & Plywood Prices",
  fb_figure_no  = "11.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = NULL,
  fb_variable  = c("HW_Lumber","HW_Plywood","SW_Lumber","SW_Plywood"),
  fb_facet1  = "variable"
)
```
