---
title: "FASOM Results"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: TRUE
    toc_depth: 3
    code_folding: "hide"
    number_sections: TRUE
---

```{r setup, include=FALSE}
devtools::load_all(".")
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 10, fig.height = 6, dpi = 150)
```

```{r setup-filters, include=FALSE}
# Set to NULL to include all files, or specify filenames to restrict the report.
options(telescope.active_files = c("V43t6_Ag.gdx", "V43t6_For.gdx"))
```

```{r process-data, include=FALSE}
# Process GDX files to standard CSV format (skips if files already exist).
# Set force = TRUE to re-process after data updates.
process_fasom_gdx(force = FALSE)
```

```{r helpers}
# GHG Pool mapping: variable -> pool label (for ghg_report and ghg_regional)
.ghg_pool_dt <- read.csv(here::here("data-raw", "VariableMapping", "ghg_pool_map.csv"))
GHG_POOL_MAP <- setNames(.ghg_pool_dt$ghg_pool, .ghg_pool_dt$variable)

# Commodity group lookup for ag_balance (acompareBalancep)
.comm_dt <- read.csv(here::here("data-raw", "VariableMapping", "commodity_group.csv"))
CROPS_COMMODITIES     <- .comm_dt$commodity[.comm_dt$group == "Crops"]
LIVESTOCK_COMMODITIES <- .comm_dt$commodity[.comm_dt$group == "Livestock"]
```

```{r load-data, message=FALSE, warning=FALSE}
library(data.table)
library(dplyr)

# Helper: resolve path within package dataset directory
ds_path <- function(rel) {
  file.path(system.file("input", "dataset", package = "telescope"), rel)
}

carbon_price  <- dataset_access("FASOM/carbon_price.csv") |>
  select(-source_filename)

# ghg_summary.csv > 50 MB — use fread
ghg_summary   <- fread(ds_path("FASOM/ghg_summary.csv")) |>
  as_tibble()

ghg_report    <- dataset_access("FASOM/ghg_report.csv") |>
  select(-source_filename) |>
  mutate(ghg_pool = GHG_POOL_MAP[variable])

ag_strategies <- dataset_access("FASOM/ag_strategies.csv") |>
  select(-source_filename)

# ag_summary.csv > 50 MB — use fread
ag_summary    <- fread(ds_path("FASOM/ag_summary.csv")) |>
  as_tibble()

# New Ag datasets (actual calendar years — no period conversion)
ag_balance    <- dataset_access("FASOM/ag_balance.csv") |>
  select(-source_filename)

ag_proc_biod  <- dataset_access("FASOM/ag_proc_biod.csv") |>
  select(-source_filename)

ag_proc_elec  <- dataset_access("FASOM/ag_proc_elec.csv") |>
  select(-source_filename)

ag_proc_eth   <- dataset_access("FASOM/ag_proc_eth.csv") |>
  select(-source_filename)

for_product_price <- dataset_access("FASOM/for_product_price.csv") |>
  select(-source_filename)

total_acres   <- dataset_access("FASOM/total_acres.csv") |>
  select(-source_filename)

nat_log_harvest <- dataset_access("FASOM/nat_log_harvest.csv") |>
  select(-source_filename)

mfg_output    <- dataset_access("FASOM/mfg_output.csv") |>
  select(-source_filename)

recycling_output <- dataset_access("FASOM/recycling_output.csv") |>
  select(-source_filename)

land_transfer <- dataset_access("FASOM/land_transfer.csv") |>
  select(-source_filename)

# total_for_acres.csv 31 MB — within threshold, use dataset_access
total_for_acres <- dataset_access("FASOM/total_for_acres.csv") |>
  select(-source_filename)

# chk_eq_landbalance.csv > 50 MB — use fread
chk_eq_landbalance <- fread(ds_path("FASOM/chk_eq_landbalance.csv")) |>
  as_tibble()
```

# Carbon Prices {#carbon-prices}

*Source: Carbon_Prices.twb — data: carbon_price.csv*
## Carbon Price Detail {#cp-sheet1-2}

```{r cp-sheet1-2}
# Tableau: Carbon_Prices.twb / Sheet 1 (2)
# Rows: Scenario; Year (crosstab view), Color: Scenario
# Filter: Model=V43t6_Ag, Scenario≠BASE, Year=2020–2050
# FLAG: exploratory — duplicate layout, rendered as line chart
plotting(
  df         = carbon_price |> mutate(value = value / (44 / 12)) |> filter(scenario != "BASE"),
  figtype    = "timeseries",
  fb_title_name = "Carbon Price (2020–2050)",
  fb_figure_no  = "1.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2050",
  fb_scenarios = NULL,
  fb_variable  = NULL
)
```

# GHG Summary — National {#ghg-summary}

*Source: gcomparesumGHGreport.twb — data: ghg_summary.csv*

```{r ghg-summary-base-data}
# Base subset used by most gcomparesumGHGreport worksheets
ghg_sum_annual <- ghg_summary |>
  filter(set == "annualflux", gas == "carbondioxideeq", category == "AllTotal")
ghg_sum_level  <- ghg_summary |>
  filter(set == "level", gas == "carbondioxideeq", category == "AllTotal")
```

## BR FLUX — Stacked Annual Flux {#ghg-sum-brflux}

```{r ghg-sum-brflux}
# Tableau: gcomparesumGHGreport.twb / BR FLUX
# Rows: Scenario; SUM(Value)/1000, Cols: Year, Color: GHG Type
# Filter: GHG Measure=annualflux, GHG=carbondioxideeq, GHG Group=AllTotal,
#         Model=V43t6_Ag, Scenario=BASE, Year=2020–2065
br_flux_df <- 
  ghg_sum_annual %>%
  mutate(value = value / 1000) %>%
  filter(!(variable %in% c("TotalNetEmis"))) %>%
  filter(!grepl("BioElec", variable)) %>%
  filter(!grepl("Biodiesel", variable)) %>% 
  filter(!grepl("Ethl", variable)) %>% 
  mutate(highlevel = str_extract(variable, "[^_]+")) %>% 
  filter(highlevel != "Dev")

plotting(
  df         = br_flux_df,
  figtype    = "stacked_bar",
  fb_title_name = "Baseline Average Annual Flux",
  fb_figure_no  = "2.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "highlevel",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_y_title = "Average Annual Flux",
  fb_y_units = "Tg CO2e/year"
)
```

## BR FLUX (2) — Annual Flux by Scenario {#ghg-sum-brflux2}

```{r ghg-sum-brflux2}
# Tableau: gcomparesumGHGreport.twb / BR FLUX (2)
# Rows: GHG Type; Scenario, Cols: Year
# Filter: GHH Measure=annualflux, Model=V43t6_Ag, Scenario=$100at3,$20at3,$50at3,BASE
plotting(
  df         = ghg_sum_annual,
  figtype    = "timeseries",
  fb_title_name = "Annual GHG Flux — Multi-scenario",
  fb_figure_no  = "2.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE", "$20at3", "$50at3", "$100at3"),
  fb_variable  = NULL,
  fb_facet1  = "variable"
)
```

## Base flux — Baseline Stacked Bar {#ghg-sum-baseflux}

```{r ghg-sum-baseflux}
# Tableau: gcomparesumGHGreport.twb / Base flux
# Rows: Scenario; SUM(Value)/1000, Cols: Model; Year, Color: GHG Type
# Filter: GHG Measure=annualflux, GHG=carbondioxideeq, GHG Group=AllTotal,
#         Model=V43t6_IRA_Ag_AgPrice, Scenario=$100at1,$100at3,BASE
# NOTE: Model V43t6_IRA_Ag_AgPrice not in current GDX — shows V43t6_Ag data
plotting(
  df         = ghg_sum_annual |> mutate(value = value / 1000),
  figtype    = "stacked_bar",
  fb_title_name = "Annual GHG Flux — Baseline by Model",
  fb_figure_no  = "2.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE", "$100at1", "$100at3"),
  fb_variable  = NULL
)
```

## Base flux (2) — Line by Model {#ghg-sum-baseflux2}

```{r ghg-sum-baseflux2}
# Tableau: gcomparesumGHGreport.twb / Base flux (2)
# Rows: SUM(Value)/1000000, Cols: Year, Color: Model
# Filter: GHG Measure=annualflux, Model=V43t6_Ag,V43t6_IRA_Ag_AgPrice,V43t6_IRA_Ag_ForPrice,
#         Scenario=BASE
plotting(
  df         = ghg_sum_annual |> mutate(value = value / 1e6) |> filter(variable == "TotalNetEmis"),
  figtype    = "timeseries",
  fb_title_name = "Annual GHG Flux — Baseline (MMT CO2e)",
  fb_figure_no  = "2.4",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL
)
```

## Base flux (3) — Line by GHG Pool & Model {#ghg-sum-baseflux3}

```{r ghg-sum-baseflux3}
# FLAG: exploratory — model comparison (V43t5_Ag only, not in current GDX)
plotting(
  df         = ghg_sum_annual |> mutate(value = value / 1e6),
  figtype    = "timeseries",
  fb_title_name = "Annual GHG Flux — GHG Pool by Model",
  fb_figure_no  = "2.5",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2030",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_facet1  = "variable"
)
```

## Base flux (4) — Line Multi-scenario {#ghg-sum-baseflux4}

```{r ghg-sum-baseflux4}
# Tableau: gcomparesumGHGreport.twb / Base flux (4)
# Rows: SUM(Value)/1000, Cols: Model; Year, Color: Scenario
# Filter: GHG Measure=annualflux, Multi-model, Year=2020–2030
plotting(
  df         = ghg_sum_annual |> mutate(value = value / 1000) |> filter(variable == "TotalNetEmis"),
  figtype    = "timeseries",
  fb_title_name = "Annual GHG Flux — Scenarios",
  fb_figure_no  = "2.6",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2030",
  fb_scenarios = NULL,
  fb_variable  = NULL
)
```

## Base flux (5)–(8) {#ghg-sum-baseflux5-8}

```{r ghg-sum-baseflux5-8}
# FLAG: exploratory — multi-model comparison sheets 5–8
# Rendered as stacked bar for Base flux (5)/(6)/(7)/(8) equivalents
for (sc in list(
  list(title = "Base flux (5) — Stacked All Models",   fig = "2.7",  models = NULL,          scens = c("BASE")),
  list(title = "Base flux (6) — Soils Only",           fig = "2.8",  models = NULL,          scens = c("BASE")),
  list(title = "Base flux (7) — Multi-Model Baseline", fig = "2.9",  models = NULL,          scens = c("BASE")),
  list(title = "Base flux (8) — Multi-Model Scenarios",fig = "2.10", models = NULL,          scens = NULL)
)) {
  p <- plotting(
    df         = ghg_sum_annual |> mutate(value = value / 1000),
    figtype    = "stacked_bar",
    fb_title_name = sc$title,
    fb_figure_no  = sc$fig,
    fb_x       = "year",
    fb_y       = "value",
    fb_color   = "variable",
    fb_regions = NULL,
    fb_models  = sc$models,
    fb_years   = "2020-2030",
    fb_scenarios = sc$scens,
    fb_variable  = NULL
  )
  print(p)
}
```

## Remaining gcomparesumGHGreport worksheets {#ghg-sum-remaining}

```{r ghg-sum-remaining}
# Sheets 9–62 of gcomparesumGHGreport.twb cover various model/scenario/year
# combinations of the same annual-flux data.  All use ghg_sum_annual.
# FLAG: exploratory — many are sensitivity comparisons for models not in GDX

# Baseline annual flux with variable breakdown — standard view
plotting(
  df         = ghg_sum_annual |> mutate(value = value / 1000),
  figtype    = "stacked_bar",
  fb_title_name = "Annual GHG Flux — All Scenarios (1000 tCO2e)",
  fb_figure_no  = "2.11",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2065",
  fb_scenarios = NULL,
  fb_variable  = NULL
)

# Cumulative mitigation view (uses set="level")
plotting(
  df         = ghg_sum_level |> mutate(value = value / 1e6),
  figtype    = "timeseries",
  fb_title_name = "Cumulative GHG Mitigation (MMT CO2e)",
  fb_figure_no  = "2.12",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2025-2065",
  fb_scenarios = c("$20at3", "$35at3", "$50at3", "BASE"),
  fb_variable  = NULL
)
```

# GHG Report — National Detail {#ghg-report}

*Source: gcompareGHGreport.twb — data: ghg_report.csv*

## Baseline Annual Flux — Stacked Bar {#ghg-rep-baseline}

```{r ghg-rep-baseline}
# Tableau: gcompareGHGreport.twb / Baseline annual flux
# Rows: Scenario; SUM(Value_CO2e)/1000000, Cols: Model; Year
# Filter: GHG Measure=annualflux, GHG Pool≠Other, Scenario=$20at3,$50at3,BASE
ghg_rep_annual <- ghg_report |>
  filter(set == "annualflux") |>
  filter(!is.na(ghg_pool))

plotting(
  df         = ghg_rep_annual |> mutate(value = value / 1e6),
  figtype    = "stacked_bar",
  fb_title_name = "Annual GHG Flux by Type",
  fb_figure_no  = "3.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "ghg_pool",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE", "$20at3", "$50at3"),
  fb_variable  = NULL
)
```

## Baseline Annual Flux (2) — Line {#ghg-rep-baseline2}

```{r ghg-rep-baseline2}
# Tableau: gcompareGHGreport.twb / Baseline annual flux (2)
# Rows: SUM(Value_CO2e)/1000000, Cols: Model; Year, Color: Scenario
# Filter: GHH Pool=Forest_USProduct, GHG Measure=annualflux
plotting(
  df         = ghg_rep_annual |>
    filter(ghg_pool == "Forest_USProduct") |>
    mutate(value = value / 1e6),
  figtype    = "timeseries",
  fb_title_name = "Forest Products Annual Flux",
  fb_figure_no  = "3.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE", "$20at3", "$50at3"),
  fb_variable  = NULL
)
```

## Cumulative Mitigation — Stacked Bar {#ghg-rep-cumul}

```{r ghg-rep-cumul}
# Tableau: gcompareGHGreport.twb / Cumulative Mitigation
# Rows: (cumulative level), Cols: Model; Year, Color: GHG Pool
# Filter: GHG Measure=level (cumulative), Scenario≠BASE
ghg_rep_level <- ghg_report |>
  filter(set == "level") |>
  filter(!is.na(ghg_pool))

plotting(
  df         = ghg_rep_level |> mutate(value = value / 1e6),
  figtype    = "stacked_bar",
  fb_title_name = "Cumulative GHG Mitigation by Pool",
  fb_figure_no  = "3.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "ghg_pool",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2025-2065",
  fb_scenarios = c("$20at3", "$35at3", "$50at3"),
  fb_variable  = NULL
)
```

## Forest Flux Line {#ghg-rep-forestflux}

```{r ghg-rep-forestflux}
# Tableau: gcompareGHGreport.twb / Forest flux line
# Filter: GHH Pool≠Ag CO2,Crop Non-CO2,Livestock Non-CO2,Soils, GHG Measure=annualflux
plotting(
  df         = ghg_rep_annual |>
    filter(ghg_pool %in% c("Afforestation", "Forest Management", "Forest_USProduct")) |>
    mutate(value = value / 1e6),
  figtype    = "timeseries",
  fb_title_name = "Forest GHG Flux",
  fb_figure_no  = "3.4",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE", "$20at3", "$35at3", "$50at3", "$5at3"),
  fb_variable  = NULL,
  fb_facet1  = "ghg_pool"
)
```

## Cumulative Mitigation Table {#ghg-rep-cumul-table}

```{r ghg-rep-cumul-table}
# Tableau: gcompareGHGreport.twb / cumulative mit table (4)
# Rows: (level), Cols: Model; Year, Color: Scenario
# Filter: GHG Measure=level, Scenario≠BASE
# FLAG: exploratory — crosstab table format
plotting(
  df         = ghg_rep_level |>
    filter(!is.na(ghg_pool)) |>
    group_by(year, scenario, model) |>
    summarise(value = sum(value, na.rm = TRUE) / 1e6, .groups = "drop") |>
    mutate(variable = "Total"),
  figtype    = "timeseries",
  fb_title_name = "Cumulative Mitigation Total",
  fb_figure_no  = "3.5",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2065",
  fb_scenarios = c("$20at3", "$35at3", "$50at3", "$5at3"),
  fb_variable  = NULL
)
```

# Ag Mitigation Strategies {#ag-strat}

*Source: gcomparenatstrategies.twb — data: ag_strategies.csv*

## Dairy BST {#ag-strat-dairybst}

```{r ag-strat-dairybst}
# Tableau: gcomparenatstrategies.twb / Dairy BST
# Rows: Value, Cols: Year, Color: Scenario
# Filter: Measure=NFertIntensity, Model=V43t6_Ag,V43t6_UM_AgFor_ssp1_modev_Ag,
#         Scenario=$15at1,$20at3,$35at1,$5at1,BASE, Year=2020–2035
# NOTE: NFertIntensity is a strategy variable in ag_strategies
plotting(
  df         = ag_strategies |>
    filter(variable == "NFertIntensity"),
  figtype    = "timeseries",
  fb_title_name = "N Fert Intensity (Dairy BST proxy)",
  fb_figure_no  = "4.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2035",
  fb_scenarios = c("BASE", "$5at1", "$15at1", "$20at3", "$35at1"),
  fb_variable  = NULL
)
```

## Dairy Manure Mgt {#ag-strat-dairymanure}

```{r ag-strat-dairymanure}
# Tableau: gcomparenatstrategies.twb / Dairy Manure Mgt
# Rows: Model; SUM(Value)/1000, Cols: Year, Color: Scenario
# Filter: Measure=DairyManureMgt
plotting(
  df         = ag_strategies |>
    filter(variable == "DairyManureMgt") |>
    mutate(value = value / 1000),
  figtype    = "timeseries",
  fb_title_name = "Dairy Manure Management",
  fb_figure_no  = "4.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2065",
  fb_scenarios = NULL,
  fb_variable  = NULL
)
```

## Hog Manure Mgt {#ag-strat-hogmanure}

```{r ag-strat-hogmanure}
# Tableau: gcomparenatstrategies.twb / Hog Manure Mgt
# Rows: Model; SUM(Value)/2000, Cols: Year, Color: Scenario
# Filter: Measure=HogFinished
plotting(
  df         = ag_strategies |>
    filter(variable == "HogFinished") |>
    mutate(value = value / 2000),
  figtype    = "timeseries",
  fb_title_name = "Hog Manure Management (Head / 2000)",
  fb_figure_no  = "4.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2065",
  fb_scenarios = NULL,
  fb_variable  = NULL
)
```

## Hog Manure Mgt (2) — Bar {#ag-strat-hogmanure2}

```{r ag-strat-hogmanure2}
# Tableau: gcomparenatstrategies.twb / Hog Manure Mgt (2)
# Rows: Value, Cols: Scenario; Year, Color: (none)
# Filter: Measure=FeedlotCTotal
plotting(
  df         = ag_strategies |>
    filter(variable == "FeedlotCTotal"),
  figtype    = "bar",
  fb_title_name = "Feedlot Commercial Total",
  fb_figure_no  = "4.4",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2065",
  fb_scenarios = NULL,
  fb_variable  = NULL
)
```

# Ag Summary {#ag-summary}

*Source: acompareAgSummary.twb — data: ag_summary.csv*

```{r ag-sum-setup}
# Convenience subsets
ag_sum_landuse  <- ag_summary |> filter(category == "Agricultural Land Use")
ag_sum_landtype <- ag_summary |> filter(category == "Ag Crop Land Use")
ag_sum_cropall  <- ag_summary |> filter(category == "Agricultural Crop All Acres")
ag_sum_cropbrk  <- ag_summary |> filter(category == "Agricultural Crop Broken out Acres")
ag_sum_tillage <- ag_summary |> filter(category == "Agricultural Tillage Use")
ag_sum_livherd <- ag_summary |> filter(category == "Agricultural Livestock Herd")
ag_sum_cropyld <- ag_summary |> filter(category %in% c("Agricultural Crop All Yield",
                                                         "Agricultural Crop Broken Out Yield"))
ag_sum_enviro  <- ag_summary |> filter(category == "Environmental Measures")
```

## Acres — Cropland by Model {#ag-sum-acres}

```{r ag-sum-acres}
# Tableau: acompareAgSummary.twb / Acres
# Rows: Measure2(group); SUM(Value)/1000, Cols: Model; Year, Color: Scenario
# Filter: Measure2(group)=Corn, Measure1=Agricultural Crop All Acres,
#         Model=V43t6_gwp_Ag, Region=CB
plotting(
  df         = ag_sum_cropall |>
    filter(region == "CB") |>
    filter(subcategory %in% c("Barley","Corn","Cotton","Rice","Soybeans",
                               "DurumWheat","HardRedSpringWheat",
                               "HardRedWinterWheat","SoftRedWinterWheat",
                               "SoftWhiteWheat")) |>
    mutate(value = value / 1000),
  figtype    = "timeseries",
  fb_title_name = "Crop Acres — CB Region",
  fb_figure_no  = "5.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE", "$100at3"),
  fb_variable  = NULL,
  fb_facet1  = "subcategory"
)
```

## Acres (2) — Cropland by Scenario {#ag-sum-acres2}

```{r ag-sum-acres2}
# Filter: Measure2(group)=Corn, Measure1=Ag Crop Land Use, Model=V43t6_Ag,
#         Region≠US (regional)
plotting(
  df         = ag_sum_cropall |>
    filter(region != "US") |>
    filter(subcategory %in% c("Barley","Corn","Cotton","Rice","Soybeans",
                               "DurumWheat","HardRedSpringWheat",
                               "HardRedWinterWheat","SoftRedWinterWheat",
                               "SoftWhiteWheat")) |>
    mutate(value = value / 1000),
  figtype    = "timeseries",
  fb_title_name = "Crop Acres — Regional",
  fb_figure_no  = "5.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE", "$100at3"),
  fb_variable  = NULL,
  fb_facet1  = "region"
)
```

## Acres (3) — Land Use Cropland All Regions {#ag-sum-acres3}

```{r ag-sum-acres3}
# Measure1=Agricultural Land Use, Measure2=Cropland, Region≠US
plotting(
  df         = ag_sum_landuse |>
    filter(subcategory == "Cropland", region != "US") |>
    mutate(value = value / 1000),
  figtype    = "timeseries",
  fb_title_name = "Agricultural Land Use — Cropland Regional",
  fb_figure_no  = "5.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2065",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "region"
)
```

## Acres Regional — Crop Acres by Region {#ag-sum-acres-reg}

```{r ag-sum-acres-reg}
# Measure1=Agricultural Crop All Acres, Region=CB, Scenario=BASE
plotting(
  df         = ag_sum_cropall |>
    filter(region == "CB") |>
    filter(subcategory %in% c("Barley","Corn","Cotton","Rice","Soybeans",
                               "DurumWheat","HardRedSpringWheat",
                               "HardRedWinterWheat","SoftRedWinterWheat",
                               "SoftWhiteWheat")) |>
    mutate(value = value / 1000),
  figtype    = "timeseries",
  fb_title_name = "Crop Acres — CB Region Baseline",
  fb_figure_no  = "5.6",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "subcategory",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL
)
```

## Ag Diesel — Bar {#ag-sum-diesel}

```{r ag-sum-diesel}
# Tableau: acompareAgSummary.twb / Ag Diesel
# Rows: Measure1; sum, Cols: Scenario, Color: Measure2
# Filter: Measure1=Environmental Measures, Measure2=QDiesel, Model=V43t6_Ag, Year=2050
plotting(
  df         = ag_sum_enviro |>
    filter(subcategory == "QDiesel", year == 2050),
  figtype    = "bar",
  fb_title_name = "Ag Diesel Use (2050)",
  fb_figure_no  = "5.7",
  fb_x       = "scenario",
  fb_y       = "value",
  fb_color   = "subcategory",
  fb_regions = c("US"),
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2050-2050",
  fb_scenarios = NULL,
  fb_variable  = NULL
)
```

## Ag Mitigation Activities — Dot Plot {#ag-sum-mitact}

```{r ag-sum-mitact}
# Tableau: acompareAgSummary.twb / Ag Mitigation Activities
# Rows: Measure2; Model, Cols: Value
# Filter: Measure1=Ag Crop Land Use,... (multiple), Model=V43t6_Ag, Region=US,
#         Scenario≠BASE, Year=2050
# FLAG: exploratory — dot plot rendered as bar for V43t6_Ag
exclude_measure2 <- c("alllanduse","AnimalUnitsCowCalf","AnimalUnitsDairy",
                       "AnimalUnitsHeiferCalfStocker","AnimalUnitsHeiferYearlingStocker",
                       "AnimalUnitsSheep","AnimalUnitsSteerCalfStocker",
                       "AnimalUnitsSteerYearlingStocker","Barley","Broiler")
plotting(
  df         = ag_summary |>
    filter(category %in% c("Ag Crop Land Use","Agricultural Crop Broken out Acres",
                             "Agricultural Livestock Herd","Agricultural Tillage Use",
                             "Environmental Measures")) |>
    filter(!subcategory %in% exclude_measure2) |>
    filter(year == 2050, region == "US"),
  figtype    = "bar",
  fb_title_name = "Ag Mitigation Activities (2050)",
  fb_figure_no  = "5.8",
  fb_x       = "value",
  fb_y       = "subcategory",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2050-2050",
  fb_scenarios = NULL,
  fb_variable  = NULL
)
```

## Ag Mitigation Activities (2) — Time Series {#ag-sum-mitact2}

```{r ag-sum-mitact2}
# FLAG: exploratory — time series of mitigation activities
plotting(
  df         = ag_summary |>
    filter(category %in% c("Ag Crop Land Use","Agricultural Crop Broken out Acres",
                             "Agricultural Tillage Use","Environmental Measures")) |>
    filter(!subcategory %in% c(exclude_measure2, "Corn")) |>
    filter(region == "US"),
  figtype    = "timeseries",
  fb_title_name = "Ag Mitigation Activities Time Series",
  fb_figure_no  = "5.9",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2015-2065",
  fb_scenarios = c("$5at1", "$20at3", "$50at3", "BASE"),
  fb_variable  = NULL,
  fb_facet1  = "subcategory"
)
```

## Corn Yield — Time Series {#ag-sum-corn}

```{r ag-sum-corn}
# Tableau: acompareAgSummary.twb / Corn
# Rows: Measure1; Measure2; Measure3; SUM(Value)/1000, Cols: Model; Year, Color: Scenario
# Filter: Measure2=Corn, Model=V43t6_CB_gwp_Ag,V43t6_gwp_Ag, Region≠US
# NOTE: V43t6_CB_gwp_Ag / V43t6_gwp_Ag not in current GDX — yield data is US-only
plotting(
  df         = ag_sum_cropyld |>
    filter(subcategory == "Corn", region == "US") |>
    mutate(value = value / 1000),
  figtype    = "timeseries",
  fb_title_name = "Corn Yield (US)",
  fb_figure_no  = "5.10",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2065",
  fb_scenarios = NULL,
  fb_variable  = NULL
)
```

## Tillage — Bar {#ag-sum-tillage}

```{r ag-sum-tillage}
# Tableau: acompareAgSummary.twb / Tillage
# Rows: Model; Scenario, Cols: Value
# Filter: Measure1=Agricultural Tillage Use, Model=V43t6_Ag, Region=US, Year=2050
plotting(
  df         = ag_sum_tillage |>
    filter(region == "US", year == 2050),
  figtype    = "bar",
  fb_title_name = "Tillage Practice Mix (2050)",
  fb_figure_no  = "5.14",
  fb_x       = "value",
  fb_y       = "subcategory",
  fb_color   = "subcategory",
  fb_regions = c("US"),
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2050-2050",
  fb_scenarios = NULL,
  fb_variable  = NULL
)
```

## Tillage (3) — Zero Tillage Time Series {#ag-sum-tillage3}

```{r ag-sum-tillage3}
# Rows: Measure2; Value, Cols: Scenario; Year, Color: Model
# Filter: Measure1=Agricultural Tillage Use, Measure2=Zero, Region=US
plotting(
  df         = ag_sum_tillage |>
    filter(region == "US", subcategory == "Zero"),
  figtype    = "timeseries",
  fb_title_name = "Zero-Tillage Acres",
  fb_figure_no  = "5.15",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2065",
  fb_scenarios = NULL,
  fb_variable  = NULL
)
```

## Tillage (4) — Area Chart {#ag-sum-tillage4}

```{r ag-sum-tillage4}
# FLAG: exploratory — area chart of tillage, V43t6_gwp_Ag only
plotting(
  df         = ag_sum_tillage |>
    filter(region == "US") |>
    mutate(value = value / 1000),
  figtype    = "stacked_bar",
  fb_title_name = "Tillage Area (stacked)",
  fb_figure_no  = "5.16",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "subcategory",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2050",
  fb_scenarios = c("$100at1"),
  fb_variable  = NULL
)
```

## Yield — Crop Yield Time Series {#ag-sum-yield}

```{r ag-sum-yield}
# Rows: Measure2(group); Value, Cols: Year, Color: Scenario
# Filter: Measure1=Agricultural Crop All Yield, Measure2=Corn,Soybeans,Wheat
plotting(
  df         = ag_sum_cropyld |>
    filter(subcategory %in% c("Corn","Soybeans",
                               "DurumWheat","HardRedSpringWheat",
                               "HardRedWinterWheat","SoftRedWinterWheat",
                               "SoftWhiteWheat")),
  figtype    = "timeseries",
  fb_title_name = "Crop Yield — Corn, Soybeans, Wheat",
  fb_figure_no  = "5.17",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2065",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "subcategory"
)
```

## Remaining acompareAgSummary Sheets {#ag-sum-remaining}

```{r ag-sum-remaining}
# FLAG: exploratory — sheets 12–44 are sensitivity comparisons
# Sheets 12 (Corn acres), 13 (Corn acres scenarios), 14–22 (crop/irrig/rice bars),
# 23–44 (tillage detail, yield, index numbers, etc.)
# Rendered as representative time series below

# Rice area bar chart (sheet 22)
plotting(
  df         = ag_sum_cropbrk |>
    filter(subcategory == "Rice", year == 2050, region == "US"),
  figtype    = "bar",
  fb_title_name = "Rice Area (2050)",
  fb_figure_no  = "5.22",
  fb_x       = "scenario",
  fb_y       = "value",
  fb_color   = "subcategory",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2050-2050",
  fb_scenarios = NULL,
  fb_variable  = NULL
)

# N Fertilizer Detail bar (sheet 20)
plotting(
  df         = ag_sum_enviro |>
    filter(subcategory %in% c("Diesel","Gasoline","NutNit","NutPho","NutPot","Water"),
           year == 2050, region == "US"),
  figtype    = "bar",
  fb_title_name = "Environmental Measures (2050)",
  fb_figure_no  = "5.20",
  fb_x       = "scenario",
  fb_y       = "value",
  fb_color   = "subcategory",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2050-2050",
  fb_scenarios = NULL,
  fb_variable  = NULL
)

# Livestock herd (sheet 34)
plotting(
  df         = ag_sum_livherd |>
    filter(subcategory %in% c("Broiler","Dairy","Fed Beef Animals","PigFinishing","Sheep")),
  figtype    = "timeseries",
  fb_title_name = "Livestock Herd",
  fb_figure_no  = "5.34",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2050",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_facet1  = "subcategory"
)
```

# Ag Balance Sheet {#ag-balance}

*Source: acompareBalancep.twb — data: ag_balance.csv*

```{r ag-bal-setup}
# Commodity groups derived from ag_balance ALLI values
crops_in_data <- unique(ag_balance$commodity[
  ag_balance$commodity %in% CROPS_COMMODITIES])
livestock_in_data <- unique(ag_balance$commodity[
  ag_balance$commodity %in% LIVESTOCK_COMMODITIES])
```

## Average Wheat Price {#ag-bal-wheat-price}

```{r ag-bal-wheat-price}
# Tableau: acompareBalancep.twb / Average Wheat Price
# Rows: Commodity; Value (price), Cols: Model; Year, Color: Scenario
# Filter: Commodity group=Crops, Measure=PriceX100
# NOTE: Tableau computed AVG(Value)/100 to get $/unit; we replicate here
plotting(
  df         = ag_balance |>
    filter(variable == "PriceX100",
           commodity %in% c("DurumWheat","HardRedSpringWheat","HardRedWinterWheat",
                              "SoftRedWinterWheat","SoftWhiteWheat")) |>
    mutate(value = value / 100),
  figtype    = "timeseries",
  fb_title_name = "Wheat Price ($/unit)",
  fb_figure_no  = "6.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2015-2100",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "commodity"
)
```

## Dom-dem — Crops Domestic Demand {#ag-bal-domdem-crops}

```{r ag-bal-domdem-crops}
# Rows: Commodity1(group); Converted Value, Cols: Scenario; Year, Color: Model
# Filter: Commodity group=Crops, Measure=Dom-Demand
plotting(
  df         = ag_balance |>
    filter(variable == "Dom-Demand",
           commodity %in% crops_in_data),
  figtype    = "timeseries",
  fb_title_name = "Domestic Demand — Crops",
  fb_figure_no  = "6.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2100",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "commodity"
)
```

## Dom-dem 2 — Livestock Domestic Demand {#ag-bal-domdem-livestock}

```{r ag-bal-domdem-livestock}
# Filter: Commodity group=Livestock, Measure=Dom-Demand, Model=V43t6_Ag
plotting(
  df         = ag_balance |>
    filter(variable == "Dom-Demand",
           !commodity %in% crops_in_data),
  figtype    = "timeseries",
  fb_title_name = "Domestic Demand — Livestock",
  fb_figure_no  = "6.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2015-2100",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "commodity"
)
```

## Export — Livestock Exports {#ag-bal-export}

```{r ag-bal-export}
# Filter: Commodity group=Livestock, Measure=Export
plotting(
  df         = ag_balance |>
    filter(variable == "Export",
           !commodity %in% crops_in_data),
  figtype    = "timeseries",
  fb_title_name = "Exports — Livestock",
  fb_figure_no  = "6.4",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2100",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "commodity"
)
```

## Price — Crop Prices {#ag-bal-price}

```{r ag-bal-price}
# Filter: Commodity group=Crops, Measure=PriceX100, Scenario=BASE
plotting(
  df         = ag_balance |>
    filter(variable == "PriceX100",
           commodity %in% crops_in_data) |>
    mutate(value = value / 100),
  figtype    = "timeseries",
  fb_title_name = "Crop Prices — Baseline",
  fb_figure_no  = "6.7",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2100",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_facet1  = "commodity"
)
```

## Price 2 — Livestock Prices {#ag-bal-price2}

```{r ag-bal-price2}
# Filter: Commodity group=Livestock, Measure=PriceX100, Model=V43t6_Ag
plotting(
  df         = ag_balance |>
    filter(variable == "PriceX100",
           !commodity %in% crops_in_data) |>
    mutate(value = value / 100),
  figtype    = "timeseries",
  fb_title_name = "Livestock Prices",
  fb_figure_no  = "6.8",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2015-2100",
  fb_scenarios = c("$50at3"),
  fb_variable  = NULL,
  fb_facet1  = "commodity"
)
```

## Production — Soybean Production {#ag-bal-production}

```{r ag-bal-production}
# Filter: Commodity=SoybeanMeal, Measure≠Excess,Export,PriceX100,...
plotting(
  df         = ag_balance |>
    filter(commodity == "SoybeanMeal",
           !variable %in% c("Excess","Export","PriceX100","Proc-Use","Proc-Yld","Prod-Use")),
  figtype    = "timeseries",
  fb_title_name = "Soybean Meal Balance",
  fb_figure_no  = "6.11",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2015-2100",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "variable"
)
```

## Remaining acompareBalancep Sheets {#ag-bal-remaining}

```{r ag-bal-remaining}
# FLAG: exploratory — scatter plots and auto-type sheets 9–15
# Sheet 13: Commodity; Scenario; Year by Measure and Model
plotting(
  df         = ag_balance |>
    filter(variable %in% c("PriceX100","Production")) |>
    mutate(value = ifelse(variable == "PriceX100", value / 100, value)),
  figtype    = "timeseries",
  fb_title_name = "Price & Production Overview",
  fb_figure_no  = "6.13",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2015-2065",
  fb_scenarios = NULL,
  fb_variable  = c("PriceX100","Production","Dom-Demand","Export"),
  fb_facet1  = "variable"
)
```

# Ag Processing — Biodiesel {#ag-proc-biod}

*Source: acompareregagprocessbiod.twb — data: ag_proc_biod.csv*

## Sheet 1 — Biodiesel by Process {#ag-biod-sheet1}

```{r ag-biod-sheet1}
# Tableau: acompareregagprocessbiod.twb / Sheet 1
# Rows: Value, Cols: Model; Year, Color: Proc
# Filter: Model=V43t6_Ag, Proc≠Make_Tot_Biodiesel_from_BD, Region=Total, Scenario=BASE
plotting(
  df         = ag_proc_biod |>
    filter(region == "Total",
           variable != "Make_Tot_Biodiesel_from_BD"),
  figtype    = "timeseries",
  fb_title_name = "Biodiesel Production by Process",
  fb_figure_no  = "7.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2050",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL
)
```

## Sheet 1 (2) — Biodiesel Aggregated {#ag-biod-sheet1-2}

```{r ag-biod-sheet1-2}
# FLAG: exploratory — same as Sheet 1 but aggregated (sum across processes)
plotting(
  df         = ag_proc_biod |>
    filter(region == "Total",
           variable != "Make_Tot_Biodiesel_from_BD") |>
    group_by(year, scenario, model, region) |>
    summarise(value = sum(value, na.rm = TRUE), .groups = "drop") |>
    mutate(variable = "Total Biodiesel"),
  figtype    = "timeseries",
  fb_title_name = "Total Biodiesel Production",
  fb_figure_no  = "7.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2050",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL
)
```

# Ag Processing — Electricity {#ag-proc-elec}

*Source: acompareregagprocesselec.twb — data: ag_proc_elec.csv*

## Levels — Electricity by Process {#ag-elec-levels}

```{r ag-elec-levels}
# Tableau: acompareregagprocesselec.twb / levels
# Rows: Value, Cols: Model; Year, Color: Proc
# Filter: Scenario=BASE
plotting(
  df         = ag_proc_elec |>
    filter(region == "Total"),
  figtype    = "timeseries",
  fb_title_name = "Electricity from Bioenergy by Process",
  fb_figure_no  = "8.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2015-2050",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL
)
```

## Levels (2) — Electricity Grouped {#ag-elec-levels2}

```{r ag-elec-levels2}
# Rows: Value, Cols: Model; Year, Color: Proc(group)
plotting(
  df         = ag_proc_elec |>
    filter(region == "Total"),
  figtype    = "timeseries",
  fb_title_name = "Electricity from Bioenergy — Grouped",
  fb_figure_no  = "8.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2050",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL
)
```

## Diff b/w 2100 — Difference from 2100 Level {#ag-elec-diff2100}

```{r ag-elec-diff2100}
# FLAG: exploratory — requires WINDOW function (difference from terminal period)
# Approximate: show levels for all scenarios
plotting(
  df         = ag_proc_elec,
  figtype    = "timeseries",
  fb_title_name = "Bioelectricity Levels — All Scenarios",
  fb_figure_no  = "8.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2050",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL
)
```

## Levels (3) — Electricity All Scenarios {#ag-elec-levels3}

```{r ag-elec-levels3}
plotting(
  df         = ag_proc_elec |>
    group_by(year, scenario, model) |>
    summarise(value = sum(value, na.rm = TRUE), .groups = "drop") |>
    mutate(variable = "Total Bioelectricity"),
  figtype    = "timeseries",
  fb_title_name = "Total Bioelectricity Production",
  fb_figure_no  = "8.6",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2015-2050",
  fb_scenarios = NULL,
  fb_variable  = NULL
)
```

# Ag Processing — Ethanol {#ag-proc-eth}

*Source: acompareregagprocethanol.twb — data: ag_proc_eth.csv*

## Sheet 1 — Ethanol by Process {#ag-eth-sheet1}

```{r ag-eth-sheet1}
# Tableau: acompareregagprocethanol.twb / Sheet 1
# Rows: Value, Cols: Model; Year, Color: Process
plotting(
  df         = ag_proc_eth |>
    filter(region == "Total"),
  figtype    = "timeseries",
  fb_title_name = "Ethanol Production by Process",
  fb_figure_no  = "9.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2015-2100",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL
)
```

# Land Balance Check {#chk-landbalance}

*Source: chk_eq_landbalance.twb — data: chk_eq_landbalance.csv*

```{r chk-landbal-setup}
# Pre-aggregate: sum over site_class and ownership for cleaner visualisation
chk_lb <- chk_eq_landbalance |>
  filter(scenario == "Base") |>
  group_by(year, region, forest_type, variable, model) |>
  summarise(value = sum(value, na.rm = TRUE), .groups = "drop") |>
  mutate(scenario = "Base")
```

## Demand to Ag by Forest Type {#chk-lb-demand-toag}

```{r chk-lb-demand-toag}
# Tableau: chk_eq_landbalance.twb / demand to ag by for_type
# Rows: Measure; Value, Cols: Model; Year, Color: ForType
# Filter: Measure=demand_toag, Measure≠demand_todev, Scenario=Base
plotting(
  df         = chk_lb |>
    filter(variable == "demand_toag"),
  figtype    = "stacked_bar",
  fb_title_name = "Land Demand — To Agriculture by Forest Type",
  fb_figure_no  = "10.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "forest_type",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2100",
  fb_scenarios = c("Base"),
  fb_variable  = NULL
)
```

## Overview — All Measures {#chk-lb-overview}

```{r chk-lb-overview}
# Tableau: chk_eq_landbalance.twb / overview
# Rows: Measure; Value, Cols: Year, Color: Model
# Filter: Measure≠demand_todev, Scenario=Base
plotting(
  df         = chk_lb |>
    filter(variable != "demand_todev") |>
    group_by(year, variable, scenario, model) |>
    summarise(value = sum(value, na.rm = TRUE), .groups = "drop"),
  figtype    = "timeseries",
  fb_title_name = "Land Balance Check — All Measures",
  fb_figure_no  = "10.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2100",
  fb_scenarios = c("Base"),
  fb_variable  = NULL,
  fb_facet1  = "variable"
)
```

## Supply Affor by Forest Type {#chk-lb-supply-affor}

```{r chk-lb-supply-affor}
# Tableau: chk_eq_landbalance.twb / supply affor by for_type
# Rows: Measure; Value, Cols: Model; Year, Color: ForType
# Filter: Measure=supply_affor, Scenario=Base
plotting(
  df         = chk_lb |>
    filter(variable == "supply_affor"),
  figtype    = "stacked_bar",
  fb_title_name = "Afforestation Supply by Forest Type",
  fb_figure_no  = "10.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "forest_type",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2100",
  fb_scenarios = c("Base"),
  fb_variable  = NULL
)
```

# Forest Product Prices {#for-product-prices}

*Source: For_Product_Prices.twb — data: for_product_price.csv*

## Lumber & Plywood {#for-pp-lumber}

```{r for-pp-lumber}
# Tableau: For_Product_Prices.twb / Lumber & Plywood
# Rows: Commodity; Value, Cols: Year, Color: Scenario
# Filter: Commodity=HW_Lumber,HW_Plywood,SW_Lumber,SW_Plywood
plotting(
  df         = for_product_price |>
    filter(variable %in% c("HW_Lumber","HW_Plywood","SW_Lumber","SW_Plywood")),
  figtype    = "timeseries",
  fb_title_name = "Lumber & Plywood Prices",
  fb_figure_no  = "11.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = NULL,
  fb_variable  = c("HW_Lumber","HW_Plywood","SW_Lumber","SW_Plywood"),
  fb_facet1  = "variable"
)
```

## Panels & Boards {#for-pp-panels}

```{r for-pp-panels}
# Filter: Commodity=MDF,OSB,OthPanels
plotting(
  df         = for_product_price |>
    filter(variable %in% c("MDF","OSB","OthPanels")),
  figtype    = "timeseries",
  fb_title_name = "Panels & Boards Prices",
  fb_figure_no  = "11.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = NULL,
  fb_variable  = c("MDF","OSB","OthPanels"),
  fb_facet1  = "variable"
)
```

## Paper & Pulp {#for-pp-paper}

```{r for-pp-paper}
# Filter: Commodity=Newsprint,P_W_Paper,Paperboard,Tissue
plotting(
  df         = for_product_price |>
    filter(variable %in% c("Newsprint","P_W_Paper","Paperboard","Tissue")),
  figtype    = "timeseries",
  fb_title_name = "Paper & Pulp Prices",
  fb_figure_no  = "11.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = NULL,
  fb_variable  = c("Newsprint","P_W_Paper","Paperboard","Tissue"),
  fb_facet1  = "variable"
)
```

# National Log Harvest {#nat-log-harvest}

*Source: NatLogHarvest.twb — data: nat_log_harvest.csv*

## Sheet 1 — National Log Harvest {#nlh-sheet1}

```{r nlh-sheet1}
# Tableau: NatLogHarvest.twb / Sheet 1
# Rows: Calculation (SUM(Value)/1000), Cols: Model; Year, Color: Scenario(group)
# Filter: Multi-model
plotting(
  df         = nat_log_harvest |> mutate(value = value / 1000),
  figtype    = "timeseries",
  fb_title_name = "National Log Harvest (MMBF/1000)",
  fb_figure_no  = "12.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = NULL,
  fb_variable  = NULL
)
```

## Sheet 1 (2)–(4) {#nlh-sheet1-2-4}

```{r nlh-remaining}
# FLAG: exploratory — different model/scenario combinations
for (sheet in list(
  list(title="NatLogHarvest (2) — Multi-scenario",  fig="12.2", models=NULL,       scens=NULL),
  list(title="NatLogHarvest (3) — Scenario summary",fig="12.3", models=c("V43t6_For"), scens=c("BASE")),
  list(title="NatLogHarvest (4) — UM models",       fig="12.4", models=NULL,       scens=NULL)
)) {
  p <- plotting(
    df         = nat_log_harvest |> mutate(value = value / 1000),
    figtype    = "timeseries",
    fb_title_name = sheet$title,
    fb_figure_no  = sheet$fig,
    fb_x       = "year",
    fb_y       = "value",
    fb_color   = "scenario",
    fb_regions = NULL,
    fb_models  = sheet$models,
    fb_years   = "2015-2080",
    fb_scenarios = sheet$scens,
    fb_variable  = NULL
  )
  print(p)
}
```

## Sheet 4 — V43t6 Model Comparison {#nlh-sheet4}

```{r nlh-sheet4}
# Filter: Model=V43t6_For,V43t6_gwp_For, Scenario=Base
plotting(
  df         = nat_log_harvest,
  figtype    = "timeseries",
  fb_title_name = "National Log Harvest — V43t6 Models",
  fb_figure_no  = "12.5",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2080",
  fb_scenarios = c("Base", "BASE"),
  fb_variable  = NULL
)
```

# Recycling Output {#recycling-output}

*Source: recycling_output.twb — data: recycling_output.csv*

## Sheet 1 {#ro-sheet1}

```{r ro-sheet1}
# Tableau: recycling_output.twb / Sheet 1
# Rows: Value, Cols: Year, Color: Model
# Filter: Model≠V41t2_For,V41t2L_For,V42t2_For, Scenario=Base
plotting(
  df         = recycling_output,
  figtype    = "timeseries",
  fb_title_name = "Recycling Output (1000 tons)",
  fb_figure_no  = "13.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = c("Base", "BASE"),
  fb_variable  = NULL
)
```

# Manufacturing Output {#mfg-output}

*Source: Manufacturing_Output.twb — data: mfg_output.csv*

## ALL — Bar by Commodity {#mfg-all}

```{r mfg-all}
# Tableau: Manufacturing_Output.twb / ALL
# Rows: Model; sum, Cols: Commodity, Color: Scenario
# Filter: Commodity group=BioPower,..., Model=V43t6_UM_AgFor_For,..., Scenario=$30at3, Year=2020,2035
lumber_panel_paper_bio <- c("BioPower","For_Pellets","SW_Lumber","HW_Lumber",
                              "SW_Plywood","HW_Plywood","MDF","OSB","OthPanels",
                              "Newsprint","P_W_Paper","Paperboard","Pulp_Chem",
                              "Pulp_Mech","Tissue")
plotting(
  df         = mfg_output |>
    filter(variable %in% lumber_panel_paper_bio,
           year %in% c(2020, 2035)),
  figtype    = "bar",
  fb_title_name = "Manufacturing Output by Commodity (2020 & 2035)",
  fb_figure_no  = "14.1",
  fb_x       = "variable",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2020-2035",
  fb_scenarios = NULL,
  fb_variable  = NULL
)
```

## ALL (2) — BioPower Time Series {#mfg-all2}

```{r mfg-all2}
# Filter: Commodity=BioPower
plotting(
  df         = mfg_output |>
    filter(variable == "BioPower"),
  figtype    = "timeseries",
  fb_title_name = "Biopower Output",
  fb_figure_no  = "14.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2050",
  fb_scenarios = NULL,
  fb_variable  = c("BioPower")
)
```

## Lumber and Plywood — Line {#mfg-lumber}

```{r mfg-lumber}
plotting(
  df         = mfg_output |>
    filter(variable %in% c("SW_Lumber","HW_Lumber","SW_Plywood","HW_Plywood")),
  figtype    = "timeseries",
  fb_title_name = "Lumber & Plywood Output",
  fb_figure_no  = "14.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2080",
  fb_scenarios = NULL,
  fb_variable  = c("SW_Lumber","HW_Lumber","SW_Plywood","HW_Plywood"),
  fb_facet1  = "variable"
)
```

## Panels and Boards {#mfg-panels}

```{r mfg-panels}
plotting(
  df         = mfg_output |>
    filter(variable %in% c("MDF","OSB","OthPanels")),
  figtype    = "timeseries",
  fb_title_name = "Panels & Boards Output",
  fb_figure_no  = "14.4",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = NULL,
  fb_variable  = c("MDF","OSB","OthPanels"),
  fb_facet1  = "variable"
)
```

## Pulp and Paper {#mfg-pulp}

```{r mfg-pulp}
plotting(
  df         = mfg_output |>
    filter(variable %in% c("Newsprint","P_W_Paper","Paperboard",
                             "Pulp_Chem","Pulp_Mech","Tissue")),
  figtype    = "timeseries",
  fb_title_name = "Pulp & Paper Output",
  fb_figure_no  = "14.5",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = NULL,
  fb_variable  = c("Newsprint","P_W_Paper","Paperboard","Pulp_Chem","Pulp_Mech","Tissue"),
  fb_facet1  = "variable"
)
```

## Panels (2) & Pulp (2) — Multi-scenario {#mfg-panels2-pulp2}

```{r mfg-panels2-pulp2}
# FLAG: exploratory — Scenario×Year facet views
for (grp in list(
  list(title = "Panels (2) Multi-scenario", fig = "14.6",
       vars = c("MDF","OSB","OthPanels")),
  list(title = "Pulp (2) Multi-scenario",   fig = "14.7",
       vars = c("Newsprint","P_W_Paper","Paperboard","Pulp_Chem","Pulp_Mech","Tissue"))
)) {
  p <- plotting(
    df         = mfg_output |> filter(variable %in% grp$vars),
    figtype    = "timeseries",
    fb_title_name = grp$title,
    fb_figure_no  = grp$fig,
    fb_x       = "year",
    fb_y       = "value",
    fb_color   = "model",
    fb_regions = NULL,
    fb_models  = NULL,
    fb_years   = "2015-2080",
    fb_scenarios = NULL,
    fb_variable  = grp$vars,
    fb_facet1  = "variable"
  )
  print(p)
}
```

# Total Acres {#total-acres}

*Source: Total_Acres.twb — data: total_acres.csv*

```{r ta-setup}
ta_private <- total_acres |> filter(ownership == "private")
```

## All Land Types — Baseline {#ta-all-base}

```{r ta-all-base}
# Tableau: Total_Acres.twb / All Land Types Base
# Rows: Land Type; SUM(Value)/1000, Cols: Model; Year, Color: Scenario
# Filter: Owner=private, Scenario=$100at3,BASE, Land Type (excl. dev)
plotting(
  df         = ta_private |>
    filter(!variable %in% c("DevelopedLand","CRP")) |>
    mutate(value = value / 1000),
  figtype    = "timeseries",
  fb_title_name = "Private Land Types — Baseline",
  fb_figure_no  = "15.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2060",
  fb_scenarios = c("Base", "BASE", "$100at3"),
  fb_variable  = NULL,
  fb_facet1  = "variable"
)
```

## All Land Types — Mitigation {#ta-all-mit}

```{r ta-all-mit}
plotting(
  df         = ta_private |>
    filter(!variable %in% c("CRP","DevelopedLand")) |>
    mutate(value = value / 1000),
  figtype    = "timeseries",
  fb_title_name = "Private Land Types — Mitigation Scenarios",
  fb_figure_no  = "15.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2080",
  fb_scenarios = c("Base", "BASE", "$100at3", "$20at1", "$50at1"),
  fb_variable  = NULL,
  fb_facet1  = "variable"
)
```

## All Land by Scenario {#ta-all-by-scenario}

```{r ta-all-by-scenario}
plotting(
  df         = ta_private |>
    filter(!variable %in% c("CRP Land","Developed land")) |>
    mutate(value = value / 1000),
  figtype    = "timeseries",
  fb_title_name = "Land Use by Scenario",
  fb_figure_no  = "15.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "variable"
)
```

## CB — Central Basin Land Types {#ta-cb}

```{r ta-cb}
plotting(
  df         = total_acres |>
    filter(region == "CB", !variable %in% c("CRP","CropLand_Pasture","DevelopedLand")) |>
    mutate(value = value / 1000),
  figtype    = "timeseries",
  fb_title_name = "CB Region Land Types",
  fb_figure_no  = "15.4",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "variable"
)
```

## Remaining Total_Acres Sheets {#ta-remaining}

```{r ta-remaining}
# FLAG: exploratory — sheets 5–25 cover different regions, ownership types,
# scenario groups and model comparisons
regions_for <- c("CB","GP","LS","NE","PNWE","PNWW","PSW","RM","SC","SE","SW")
for (reg in regions_for) {
  p <- plotting(
    df         = total_acres |>
      filter(region == reg, ownership == "private",
             !variable %in% c("CRP","DevelopedLand")) |>
      mutate(value = value / 1000),
    figtype    = "timeseries",
    fb_title_name = paste("Land Types —", reg),
    fb_figure_no  = paste0("15.", which(regions_for == reg) + 4),
    fb_x       = "year",
    fb_y       = "value",
    fb_color   = "scenario",
    fb_regions = NULL,
    fb_models  = c("V43t6_For"),
    fb_years   = "2015-2080",
    fb_scenarios = c("Base","BASE"),
    fb_variable  = NULL,
    fb_facet1  = "variable"
  )
  print(p)
}
```

# Total Forest Acres {#total-for-acres}

*Source: totalforacres.twb — data: total_for_acres.csv*

## PNWW Area {#tfa-pnww}

```{r tfa-pnww}
# Tableau: totalforacres.twb / PNWW area
# Rows: SUM(Value1)/1000, Cols: Scenario; Year, Color: Model
# Filter: Region=PNWW, Scenario=Base
plotting(
  df         = total_for_acres |>
    filter(region == "PNWW") |>
    mutate(value = value / 1000),
  figtype    = "timeseries",
  fb_title_name = "PNWW Forest Acres",
  fb_figure_no  = "16.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2065",
  fb_scenarios = c("Base","BASE"),
  fb_variable  = NULL,
  fb_facet1  = "variable"
)
```

## Planted Forest Levels {#tfa-planted}

```{r tfa-planted}
# Filter: For_Type=Planted_Doug-fir,Planted_OakPine,Planted_Pine,Planted_Softwood,
#         Region=all, Scenario=Base
planted_types <- c("Planted_Doug-fir","Planted_OakPine","Planted_Pine","Planted_Softwood")
plotting(
  df         = total_for_acres |>
    filter(variable %in% planted_types) |>
    mutate(value = value / 1000),
  figtype    = "timeseries",
  fb_title_name = "Planted Forest Acres",
  fb_figure_no  = "16.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2070",
  fb_scenarios = c("Base","BASE"),
  fb_variable  = planted_types,
  fb_facet1  = "variable"
)
```

## Planted Forest Diff Baseline {#tfa-planted-diff}

```{r tfa-planted-diff}
# Difference from BASE scenario for planted forests
# FLAG: exploratory — requires baseline subtraction
base_planted <- total_for_acres |>
  filter(variable %in% planted_types, scenario %in% c("Base","BASE")) |>
  select(year, region, ownership, variable, site_class, value) |>
  rename(base_value = value)

diff_planted <- total_for_acres |>
  filter(variable %in% planted_types, !scenario %in% c("Base","BASE")) |>
  left_join(base_planted,
            by = c("year","region","ownership","variable","site_class")) |>
  mutate(value = value - coalesce(base_value, 0L))

plotting(
  df         = diff_planted |>
    mutate(value = value / 1000),
  figtype    = "timeseries",
  fb_title_name = "Planted Forest Acres — Difference from Baseline",
  fb_figure_no  = "16.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2020-2070",
  fb_scenarios = NULL,
  fb_variable  = planted_types,
  fb_facet1  = "variable"
)
```

## SE Forest Types {#tfa-se}

```{r tfa-se}
# Filter: Region=SE, Scenario=Base
plotting(
  df         = total_for_acres |>
    filter(region == "SE") |>
    mutate(value = value / 1000),
  figtype    = "timeseries",
  fb_title_name = "SE Forest Types",
  fb_figure_no  = "16.4",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = c("Base","BASE"),
  fb_variable  = NULL
)
```

## Remaining totalforacres Sheets {#tfa-remaining}

```{r tfa-remaining}
# FLAG: exploratory — sheets 8–26 cover regional breakdowns and model comparisons
# Representative: all regions baseline
for (reg in c("CB","GP","LS","NE","PNWE","PSW","RM","SC","SW")) {
  p <- plotting(
    df         = total_for_acres |>
      filter(region == reg, ownership == "private") |>
      mutate(value = value / 1000),
    figtype    = "timeseries",
    fb_title_name = paste("Forest Acres —", reg),
    fb_figure_no  = paste0("16.", which(c("CB","GP","LS","NE","PNWE","PSW","RM","SC","SW") == reg) + 4),
    fb_x       = "year",
    fb_y       = "value",
    fb_color   = "variable",
    fb_regions = NULL,
    fb_models  = c("V43t6_For"),
    fb_years   = "2015-2080",
    fb_scenarios = c("Base","BASE"),
    fb_variable  = NULL
  )
  print(p)
}
```

# Land Transfer Cumulative {#land-transfer}

*Source: LandTransferCumulative.twb — data: land_transfer.csv*

> NOTE: Most worksheets filter on `Model=V43t6_UM_AgFor_NPL_For` which is not in
> the current GDX (`V43t6_For`).  Figures are implemented using available data; 
> use `fb_models = NULL` to show V43t6_For data where these models differ.

## Cropland Pasture Movement {#lt-crop-past}

```{r lt-crop-past}
# Tableau: LandTransferCumulative.twb / Cropland Pasture movement
# Filter: land_from=CropLand_Pasture, Region=all non-US, Scenario=Base
plotting(
  df         = land_transfer |>
    filter(land_from == "CropLand_Pasture",
           region != "US"),
  figtype    = "timeseries",
  fb_title_name = "Cropland-Pasture Land Movement",
  fb_figure_no  = "17.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2080",
  fb_scenarios = c("Base","BASE"),
  fb_variable  = NULL,
  fb_facet1  = "variable"
)
```

## Cropland Movement {#lt-cropland}

```{r lt-cropland}
# Filter: land_from=Cropland, land_to=ToCroplandPasture,Todevelopment,ToForest
plotting(
  df         = land_transfer |>
    filter(land_from == "Cropland",
           variable %in% c("ToCroplandPasture","Todevelopment","ToForest"),
           region != "US"),
  figtype    = "timeseries",
  fb_title_name = "Cropland to Other Uses",
  fb_figure_no  = "17.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2080",
  fb_scenarios = c("Base","BASE"),
  fb_variable  = NULL,
  fb_facet1  = "variable"
)
```

## Forest Movement {#lt-forest}

```{r lt-forest}
# Filter: land_from=ForestLand, land_to=ToCropland,..., Scenario=$15at1
plotting(
  df         = land_transfer |>
    filter(land_from == "ForestLand",
           variable %in% c("ToCropland","ToCroplandPasture","Todevelopment",
                            "ToForest","ToPasture"),
           region != "US"),
  figtype    = "timeseries",
  fb_title_name = "Forestland to Other Uses",
  fb_figure_no  = "17.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2080",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "variable"
)
```

## Pasture Movement (2) {#lt-pasture}

```{r lt-pasture}
# Filter: land_from=Cropland,CropLand_Pasture,Pasture, land_to=Todevelopment
plotting(
  df         = land_transfer |>
    filter(land_from %in% c("Cropland","CropLand_Pasture","Pasture"),
           variable == "Todevelopment",
           region != "US"),
  figtype    = "timeseries",
  fb_title_name = "Land Developed from Ag",
  fb_figure_no  = "17.4",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "model",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2080",
  fb_scenarios = c("Base","BASE"),
  fb_variable  = NULL,
  fb_facet1  = "land_from"
)
```

## Sheet 7 — Stacked Bar {#lt-sheet7}

```{r lt-sheet7}
# Filter: Region=RM, Model=V43t6_gwp_For, land_from=Cropland,ForestLand,Pasture
plotting(
  df         = land_transfer |>
    filter(region == "RM",
           land_from %in% c("Cropland","ForestLand","Pasture")) |>
    mutate(value = value / 1000),
  figtype    = "stacked_bar",
  fb_title_name = "RM Land Transfer",
  fb_figure_no  = "17.7",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "land_from",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2060",
  fb_scenarios = c("$35at3","Base","BASE"),
  fb_variable  = NULL
)
```

## Regional Forest — Stacked Bar {#lt-regional-forest}

```{r lt-regional-forest}
# Filter: land_from=ForestLand, Region=[all], Scenario=base
plotting(
  df         = land_transfer |>
    filter(land_from == "ForestLand", region != "US"),
  figtype    = "stacked_bar",
  fb_title_name = "Regional Forest Land to Other Uses",
  fb_figure_no  = "17.8",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "region",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2065",
  fb_scenarios = c("base","Base","BASE"),
  fb_variable  = NULL,
  fb_facet1  = "variable"
)
```

## Remaining LandTransfer Sheets {#lt-remaining}

```{r lt-remaining}
# FLAG: exploratory — sheets 8–18 cover land change matrices and change-from-period calcs
# Sheet 13: Todevelopment from ForestLand by region
plotting(
  df         = land_transfer |>
    filter(land_from == "ForestLand", variable == "Todevelopment") |>
    filter(region != "US"),
  figtype    = "timeseries",
  fb_title_name = "Forest to Development — Regional",
  fb_figure_no  = "17.9",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2015-2065",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "region"
)
```

# GHG Summary — UMD Variant {#ghg-sum-umd}

*Source: gcomparesumGHGreport_UMD.twb — data: ghg_summary.csv*

```{r ghg-sum-umd-setup}
# Same data as main gcomparesumGHGreport but filtered to UMD-relevant models
ghg_sum_umd <- ghg_summary |>
  filter(set == "annualflux", gas == "carbondioxideeq", category == "AllTotal")
```

## UMD Sheets 1–13 {#ghg-sum-umd-all}

```{r ghg-sum-umd-all}
# FLAG: exploratory — 13 worksheets with various model/scenario filters
# Many reference models not in GDX (V43t6_UM_AgFor_NPL_Ag, etc.)
# Representative implementation below

plotting(
  df         = ghg_sum_umd |> mutate(value = value / 1000),
  figtype    = "stacked_bar",
  fb_title_name = "GHG Summary — UMD Scenarios",
  fb_figure_no  = "18.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2065",
  fb_scenarios = NULL,
  fb_variable  = NULL
)

plotting(
  df         = ghg_sum_umd |> mutate(value = value / 1e6),
  figtype    = "timeseries",
  fb_title_name = "GHG Summary — UMD Line View",
  fb_figure_no  = "18.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2065",
  fb_scenarios = NULL,
  fb_variable  = NULL
)
```

# GHG Summary with Carbon Price {#ghg-sum-cp}

*Source: gcomparesumGHGreport_withCarbonPrice.twb — data: ghg_summary.csv + carbon_price.csv*

> NOTE: Worksheets in this workbook join GHG summary with carbon price for
> cost-effectiveness analysis.  The join is performed below; carbon price is
> appended as an annotation series.

```{r ghg-sum-cp-setup}
# Join carbon price onto ghg_summary by year and scenario
cp_join <- carbon_price |>
  mutate(value_cp = value / (44 / 12)) |>   # convert to $/tCO2e
  select(year, scenario, value_cp)

ghg_sum_cp <- ghg_sum_annual |>
  left_join(cp_join, by = c("year","scenario")) |>
  mutate(value = value / 1000)
```

## GHG with Carbon Price — Overview {#ghg-sum-cp-overview}

```{r ghg-sum-cp-overview}
# FLAG: exploratory — 20 worksheets; many require dual-axis overlays
# Representative: annual flux coloured by scenario with carbon-price annotation
plotting(
  df         = ghg_sum_cp,
  figtype    = "stacked_bar",
  fb_title_name = "Annual GHG Flux with Carbon Price Context",
  fb_figure_no  = "19.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE","$20at3","$50at3"),
  fb_variable  = NULL
)
```

# LandTransfer — V41 2100 Run {#lt-v41-2100}

*Source: LandTransferCumulative_v41_2100.twb*

> **TODO**: This workbook uses data from an older FASOM run (V41t2 2100-year horizon)
> which is not present in the current input dataset.  Implement once the corresponding
> CSV is added to `input/dataset/FASOM/`.

# Excel-Only Workbooks (TODO) {#excel-only}

The following Tableau workbooks connect to Excel files that are not part of
the current GDX-based pipeline.  Each workbook is listed with a TODO placeholder;
implement once the corresponding data is ingested into the dataset pipeline.

## Affor ReducedDefor {#todo-affor}

> **TODO** (`Affor_ReducedDefor.twb`): 3 worksheets — data source:
> `FASOM_Affor_ReducedDefor.xlsx`.  Implement once Excel data is converted to CSV.

## Ag Mitigation Strategies — Excel {#todo-agmitstrat}

> **TODO** (`agmitstrategies.twb`): 7 worksheets — data source:
> `v43t6 Land Use Mitigation Activities.xlsx`.
> Note: `gcomparenatstrategies.twb` (implemented above) uses the GDX-derived
> equivalent `ag_strategies.csv`; this workbook uses a different Excel-formatted
> source.

## Cover Crop Area {#todo-covercrop}

> **TODO** (`Cover Crop Area.twb`): 1 worksheet — data source:
> `agcrobudget_CC.xlsx`.

## Cover Crop GHG B50 {#todo-covercropghg}

> **TODO** (`CoverCropGHG_B50.twb`): 1 worksheet — data source:
> `GHG_CoverCrop_B50.xlsx` (local user path).

## FASOM Crop Budget {#todo-cropbudget}

> **TODO** (`FASOM_CropBudget.twb`): 7 worksheets — data source:
> `FASOM_CropBudget.xlsx`.

## FASOM IRA 2023 {#todo-ira}

> **TODO** (`FASOM_IRA_2_9_23.twb`): 1 worksheet — data source:
> `FASOM_IRA_2_9_23.xlsx`.

## For AEO Macro Comparison {#todo-aeo}

> **TODO** (`For_AEO_Macro_Comparison.twb`): 1 worksheet — data source:
> `AEO_Comparison.xlsx`.

## For Demand Comparison {#todo-fordemand}

> **TODO** (`For_Demand_Comparison.twb`): 5 worksheets — data source:
> `AEO_Comparison.xlsx`.

