---
title: "FASOM Results — Complex Figures"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    toc_depth: 3
    code_folding: "hide"
    number_sections: TRUE
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
devtools::load_all(".")
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 10, fig.height = 6, dpi = 150)
```

```{r setup-filters, include=FALSE}
options(telescope.active_files = c("V43t6_Ag.gdx", "V43t6_For.gdx"))
```

```{r process-data, include=FALSE}
process_fasom_gdx(force = FALSE)
```

```{r helpers}
# GHG Pool mapping: variable -> pool label (for ghg_report and ghg_regional)
.ghg_pool_dt <- read.csv(here::here("data-raw", "VariableMapping", "ghg_pool_map.csv"))
GHG_POOL_MAP <- setNames(.ghg_pool_dt$ghg_pool, .ghg_pool_dt$variable)
```

```{r load-data, message=FALSE, warning=FALSE}
library(data.table)
library(dplyr)

ds_dir <- system.file("input", "dataset", package = "telescope")

# ---- Large files loaded with fread ----
# ghg_regional.csv (>50 MB)
ghg_regional <- fread(file.path(ds_dir, "FASOM/ghg_regional.csv")) |>
  mutate(ghg_pool = GHG_POOL_MAP[variable])

# for_forest_to_mill.csv (>50 MB)
for_forest_to_mill <- fread(file.path(ds_dir, "FASOM/for_forest_to_mill.csv"))

# ---- Standard-size files ----
for_mill_to_port <- dataset_access("FASOM/for_mill_to_port.csv") |>
  select(-source_filename)

for_forest_to_port <- dataset_access("FASOM/for_forest_to_port.csv") |>
  select(-source_filename)

carbon_price <- dataset_access("FASOM/carbon_price.csv") |>
  select(-source_filename)

ghg_summary <- dataset_access("FASOM/ghg_summary.csv") |>
  select(-source_filename)
```

# GHG Regional — gcompareREportreg {#ghg-regional}

*Source: gcompareREportreg.twb — data: ghg_regional.csv + carbon_price.csv*

> These 56 worksheets provide regional breakdowns of annual GHG flux by GHG Pool,
> region, and scenario.  The `ghg_regional` dataset has >50 MB and is read with
> `data.table::fread()`.

```{r ghg-reg-setup}
# Base subsets used by most gcompareREportreg worksheets
ghg_reg_annual <- ghg_regional |>
  filter(set == "annualflux") |>
  filter(!is.na(ghg_pool))

ghg_reg_diff <- ghg_regional |>
  filter(set == "annualfluxdiffrombase") |>
  filter(!is.na(ghg_pool))
```

## Forest Pools — Regional {#ghg-reg-forest}

```{r ghg-reg-forest}
# Tableau: gcompareREportreg.twb — Forest pool worksheets
# Filter: GHH Pool=Afforestation,Forest Management,Forest Products,Forest Soils
forest_pools <- c("Afforestation","Forest Management","Forest Products","Forest Soils")

plotting(
  df         = ghg_reg_annual |>
    filter(ghg_pool %in% forest_pools) |>
    mutate(value = value / 1000),
  figtype    = "stacked_bar",
  fb_title_name = "Forest GHG Flux — Regional",
  fb_figure_no  = "20.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "ghg_pool",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_facet1  = "region"
)
```

## Ag Pools — Regional {#ghg-reg-ag}

```{r ghg-reg-ag}
# Filter: GHH Pool=Ag CO2,Ag Soils,Crop Non-CO2,Livestock Non-CO2
ag_pools <- c("Ag CO2","Ag Soils","Crop Non-CO2","Livestock Non-CO2")

plotting(
  df         = ghg_reg_annual |>
    filter(ghg_pool %in% ag_pools) |>
    mutate(value = value / 1000),
  figtype    = "stacked_bar",
  fb_title_name = "Agricultural GHG Flux — Regional",
  fb_figure_no  = "20.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "ghg_pool",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_facet1  = "region"
)
```

## All Pools — Diff from Baseline {#ghg-reg-diff}

```{r ghg-reg-diff}
# Filter: GHG Measure=annualfluxdiffrombase, Scenario≠BASE
plotting(
  df         = ghg_reg_diff |>
    mutate(value = value / 1000),
  figtype    = "stacked_bar",
  fb_title_name = "GHG Mitigation — Regional Difference from Baseline",
  fb_figure_no  = "20.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "ghg_pool",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2065",
  fb_scenarios = c("$20at3","$50at3"),
  fb_variable  = NULL,
  fb_facet1  = "region"
)
```

## Regional Timeseries — All Scenarios {#ghg-reg-ts}

```{r ghg-reg-ts}
# Aggregate all pools by region/year/scenario for total net flux
ghg_reg_total <- ghg_reg_annual |>
  group_by(year, region, scenario, model) |>
  summarise(value = sum(value, na.rm = TRUE) / 1e6, .groups = "drop") |>
  mutate(variable = "Net GHG Flux")

plotting(
  df         = ghg_reg_total,
  figtype    = "timeseries",
  fb_title_name = "Total Net GHG Flux — Regional",
  fb_figure_no  = "20.4",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_Ag"),
  fb_years   = "2020-2065",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "region"
)
```

## Remaining gcompareREportreg Worksheets {#ghg-reg-remaining}

```{r ghg-reg-remaining}
# FLAG: exploratory — 52 additional worksheets cover:
#  - individual pool timeseries by region
#  - scenario comparison views
#  - multi-model comparisons
#  - afforestation/deforestation breakouts
# Representative loop: one stacked bar per region (Baseline)

for (reg in c("CB","GP","LS","NE","PNWE","PNWW","PSW","RM","SC","SE","SW","National")) {
  p <- plotting(
    df         = ghg_reg_annual |>
      filter(region == reg, !is.na(ghg_pool)) |>
      mutate(value = value / 1000),
    figtype    = "stacked_bar",
    fb_title_name = paste("GHG Flux —", reg, "Region"),
    fb_figure_no  = paste0("20.", which(c("CB","GP","LS","NE","PNWE","PNWW","PSW","RM","SC","SE","SW","National") == reg) + 4),
    fb_x       = "year",
    fb_y       = "value",
    fb_color   = "ghg_pool",
    fb_regions = NULL,
    fb_models  = c("V43t6_Ag"),
    fb_years   = "2020-2065",
    fb_scenarios = c("BASE"),
    fb_variable  = NULL
  )
  print(p)
}
```

# GHG Regional — UMD Variant {#ghg-reg-umd}

*Source: gcompareREportreg_UMD.twb (23 sheets) and gcompareREportreg_UMD_v2.twb (28 sheets)*
*— data: ghg_regional.csv + carbon_price.csv*

> Same data as gcompareREportreg.twb but filtered to UMD-relevant models
> and scenarios.  Representative implementations below.

## UMD Forest Flux {#ghg-reg-umd-forest}

```{r ghg-reg-umd-forest}
# FLAG: exploratory — 23 + 28 worksheets filtered on models not in current GDX
plotting(
  df         = ghg_reg_annual |>
    filter(ghg_pool %in% c("Afforestation","Forest Management","Forest Products","Forest Soils")) |>
    mutate(value = value / 1000),
  figtype    = "stacked_bar",
  fb_title_name = "UMD Forest GHG Flux (available models)",
  fb_figure_no  = "21.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "ghg_pool",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_facet1  = "region"
)
```

## UMD Ag Flux {#ghg-reg-umd-ag}

```{r ghg-reg-umd-ag}
plotting(
  df         = ghg_reg_annual |>
    filter(ghg_pool %in% c("Ag CO2","Ag Soils","Crop Non-CO2","Livestock Non-CO2")) |>
    mutate(value = value / 1000),
  figtype    = "stacked_bar",
  fb_title_name = "UMD Ag GHG Flux (available models)",
  fb_figure_no  = "21.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "ghg_pool",
  fb_regions = NULL,
  fb_models  = NULL,
  fb_years   = "2020-2065",
  fb_scenarios = c("BASE"),
  fb_variable  = NULL,
  fb_facet1  = "region"
)
```

# GHG Regional — Map Workbook (TODO) {#ghg-reg-map}

*Source: gcompareREportreg_UMD_v2_Map.twb (20 sheets)*

> **TODO**: 20 worksheets use a shapefile (`FASOM_11_Current_Measures_062823.shp`)
> for choropleth mapping.  Implement once the shapefile is accessible via:
> `sf::read_sf()` and `ggplot2::geom_sf()`.

# Forest Flow — Forest to Mill {#for-forest-to-mill}

*Source: FOR_Forest_To_Mill.twb — data: for_forest_to_mill.csv (>50 MB)*

```{r for-mill-setup}
# Log type groupings used in FOR_Forest_To_Mill
# Actual values: SW_SawLogs, SW_PulpLogs, SW_LogRes, HW_SawLogs, HW_PulpLogs, HW_LogRes
softwood_logs <- c("SW_SawLogs", "SW_PulpLogs", "SW_LogRes")
hardwood_logs <- c("HW_SawLogs", "HW_PulpLogs", "HW_LogRes")
```

## Softwood to Mill — Regional {#for-mill-sw}

```{r for-mill-sw}
# Tableau: FOR_Forest_To_Mill.twb
# Rows: Value, Cols: Year, Color: Scenario
# Filter: log_type=softwood variants, Region≠Total
plotting(
  df         = for_forest_to_mill |>
    filter(log_type %in% softwood_logs) |>
    group_by(year, region, scenario, model) |>
    summarise(value = sum(value, na.rm = TRUE), .groups = "drop") |>
    mutate(variable = "Softwood"),
  figtype    = "timeseries",
  fb_title_name = "Softwood Log Harvest to Mill — Regional",
  fb_figure_no  = "22.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = c("Base","BASE"),
  fb_variable  = NULL,
  fb_facet1  = "region"
)
```

## Hardwood to Mill — Regional {#for-mill-hw}

```{r for-mill-hw}
plotting(
  df         = for_forest_to_mill |>
    filter(log_type %in% hardwood_logs) |>
    group_by(year, region, scenario, model) |>
    summarise(value = sum(value, na.rm = TRUE), .groups = "drop") |>
    mutate(variable = "Hardwood"),
  figtype    = "timeseries",
  fb_title_name = "Hardwood Log Harvest to Mill — Regional",
  fb_figure_no  = "22.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = c("Base","BASE"),
  fb_variable  = NULL,
  fb_facet1  = "region"
)
```

## Total Log Flow to Mill {#for-mill-total}

```{r for-mill-total}
plotting(
  df         = for_forest_to_mill |>
    group_by(year, region, scenario, model) |>
    summarise(value = sum(value, na.rm = TRUE), .groups = "drop") |>
    mutate(variable = "Total"),
  figtype    = "timeseries",
  fb_title_name = "Total Log Harvest to Mill",
  fb_figure_no  = "22.3",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "region"
)
```

## Log Flow by Forest Type {#for-mill-by-type}

```{r for-mill-by-type}
plotting(
  df         = for_forest_to_mill |>
    group_by(year, region, forest_type, scenario, model) |>
    summarise(value = sum(value, na.rm = TRUE), .groups = "drop") |>
    rename(variable = forest_type),
  figtype    = "stacked_bar",
  fb_title_name = "Log Flow by Forest Type",
  fb_figure_no  = "22.4",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "variable",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = c("Base","BASE"),
  fb_variable  = NULL,
  fb_facet1  = "region"
)
```

## Log Flow Multi-scenario {#for-mill-scenarios}

```{r for-mill-scenarios}
# FLAG: exploratory — 6 remaining FOR_Forest_To_Mill sheets
for (sc_grp in list(
  list(title = "Softwood Log Flow — High Carbon Price", fig = "22.5",
       logs = softwood_logs, scens = c("$50at3","$100at3")),
  list(title = "Hardwood Log Flow — High Carbon Price", fig = "22.6",
       logs = hardwood_logs, scens = c("$50at3","$100at3"))
)) {
  p <- plotting(
    df         = for_forest_to_mill |>
      filter(log_type %in% sc_grp$logs) |>
      group_by(year, region, scenario, model) |>
      summarise(value = sum(value, na.rm = TRUE), .groups = "drop") |>
      mutate(variable = "Total"),
    figtype    = "timeseries",
    fb_title_name = sc_grp$title,
    fb_figure_no  = sc_grp$fig,
    fb_x       = "year",
    fb_y       = "value",
    fb_color   = "scenario",
    fb_regions = NULL,
    fb_models  = c("V43t6_For"),
    fb_years   = "2015-2080",
    fb_scenarios = sc_grp$scens,
    fb_variable  = NULL,
    fb_facet1  = "region"
  )
  print(p)
}
```

# Forest Flow — Forest to Port {#for-forest-to-port}

*Source: For_forest_to_port.twb — data: for_forest_to_port.csv*

## Sheet 1 {#for-port-sheet1}

```{r for-port-sheet1}
# Tableau: For_forest_to_port.twb / Sheet 1
plotting(
  df         = for_forest_to_port |>
    group_by(year, region, scenario, model, variable) |>
    summarise(value = sum(value, na.rm = TRUE), .groups = "drop"),
  figtype    = "timeseries",
  fb_title_name = "Log Export — Forest to Port",
  fb_figure_no  = "23.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = NULL,
  fb_variable  = NULL,
  fb_facet1  = "region"
)
```

# Forest Flow — Mill to Port {#for-mill-to-port}

*Source: For_mill_to_port.twb — data: for_mill_to_port.csv*

## Sheet 1 — Mill to Port by Commodity {#for-mtp-sheet1}

```{r for-mtp-sheet1}
plotting(
  df         = for_mill_to_port |>
    group_by(year, region, commodity_from, scenario, model, variable) |>
    summarise(value = sum(value, na.rm = TRUE), .groups = "drop") |>
    rename(commodity = commodity_from),
  figtype    = "timeseries",
  fb_title_name = "Manufactured Products Export — Mill to Port",
  fb_figure_no  = "24.1",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = c("Base","BASE"),
  fb_variable  = NULL,
  fb_facet1  = "commodity"
)
```

## Sheet 2 — Mill to Port Regional {#for-mtp-sheet2}

```{r for-mtp-sheet2}
plotting(
  df         = for_mill_to_port |>
    group_by(year, region, region_to, scenario, model) |>
    summarise(value = sum(value, na.rm = TRUE), .groups = "drop") |>
    mutate(variable = paste(region, "→", region_to)),
  figtype    = "timeseries",
  fb_title_name = "Mill to Port — Origin–Destination",
  fb_figure_no  = "24.2",
  fb_x       = "year",
  fb_y       = "value",
  fb_color   = "scenario",
  fb_regions = NULL,
  fb_models  = c("V43t6_For"),
  fb_years   = "2015-2080",
  fb_scenarios = c("Base","BASE"),
  fb_variable  = NULL
)
```
